---
title: "Ternary"
author: "Aishwarya Maloo"
date: "11 February 2023"
date-modified: "`r Sys.Date()`"
format: html
execute: 
  echo: true
  eval: true
  warning: false
editor: visual
---

# **Installing and launching R packages**

For this exercise, two main R packages will be used in this hands-on exercise, they are:

-   [**ggtern**](http://www.ggtern.com/), a ggplot extension specially designed to plot ternary diagrams. The package will be used to plot static ternary plots.

-   [**Plotly R**](https://plot.ly/r/), an R package for creating interactive web-based graphs via plotly's JavaScript graphing library, plotly.js . The **plotly R** libary contains the *ggplotly* function, which will convert **ggplot2** figures into a Plotly object.

The code chunks below will accomplish the task.

```{r}
pacman::p_load(ggtern, plotly, tidyverse)
```

# **Data Preparation**

## **The data**

For the purpose of this hands-on exercise, the [Singapore Residents by Planning AreaSubzone, Age Group, Sex and Type of Dwelling, June 2000-2018](https://www.singstat.gov.sg/find-data/search-by-theme/population/geographic-distribution/latest-data) data will be used. The data set has been downloaded and included in the data sub-folder of the hands-on exercise folder. It is called *respopagsex2000to2018_tidy.csv* and is in csv file format.

\
**Importing Data**

To important *respopagsex2000to2018_tidy.csv* into R, ***read_csv()*** function of **readr** package will be used.

```{r}
pop_data <- read_csv("data/respopagsex2000to2018_tidy.csv") 
```

## **Preparing the Data**

Next, use the ***mutate()*** function of **dplyr** package to derive three new measures, namely: young, active, and old.

```{r}
agpop_mutated <- pop_data %>%
  mutate(`Year` = as.character(Year))%>%
  spread(AG, Population) %>%
  mutate(YOUNG = rowSums(.[4:8]))%>%
  mutate(ACTIVE = rowSums(.[9:16]))  %>%
  mutate(OLD = rowSums(.[17:21])) %>%
  mutate(TOTAL = rowSums(.[22:24])) %>%
  filter(Year == 2018)%>%
  filter(TOTAL > 0)
```

# **Plotting Ternary Diagram with R**

## **Plotting a static ternary diagram**

Use ***ggtern()*** function of **ggtern** package to create a simple ternary plot.

```{r}
ggtern(data=agpop_mutated,aes(x=YOUNG,y=ACTIVE, z=OLD)) +
  geom_point()
```

### Improving the plot

```{r}
ggtern(data=agpop_mutated, aes(x=YOUNG,y=ACTIVE, z=OLD)) +
  geom_point() +
  labs(title="Population structure, 2015") +
  theme_rgbw()
```

## **Plotting an interative ternary diagram**

The code below create an interactive ternary plot using ***plot_ly()*** function of **Plotly R**.

```{r}
label <- function(txt) {
  list(
    text = txt, 
    x = 0.1, y = 1,
    ax = 0, ay = 0,
    xref = "paper", yref = "paper", 
    align = "center",
    font = list(family = "serif", size = 15, color = "white"),
    bgcolor = "#b3b3b3", bordercolor = "black", borderwidth = 2
  )
}

axis <- function(txt) {
  list(
    title = txt, tickformat = ".0%", tickfont = list(size = 10)
  )
}

ternaryAxes <- list(
  aaxis = axis("Young"), 
  baxis = axis("Active"), 
  caxis = axis("Old")
)

plot_ly(
  agpop_mutated, 
  a = ~YOUNG, 
  b = ~ACTIVE, 
  c = ~OLD, 
  color = I("black"), 
  type = "scatterternary"
) %>%
  layout(
    annotations = label("Ternary Markers"), 
    ternary = ternaryAxes
  )
```
